---
title: "Testing Report"
author: "Mitchell Frischmeyer"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
#### CLEAR MEMORY
rm(list=ls())
#### Clear the R console
cat("\f")
#### Prevent Warnings
options(warn=-1)
```

## Modeling Klamath Operations
#### Model Start Date: 2/01/2020

This document is meant to demonstrate and visualize the difference between the Klamath Operations RiverWare Model and PA Calculator. Certain key variables present within both tools were chosen for comparison due to the amount of other variable calculations dependent upon them. Thus, these variables have the greatest probability of being the source of error within the RiverWare Model. Shown below are plots of the variable difference between the two tools as well as an indicator of when the maximum deviation occurs.

#Load Libraries
```{r echo = FALSE, warning = FALSE, message = FALSE}
#Code for testing the KROM vs the IGD Calc
#Load the Libraries
library(openxlsx)
library(tibble)
library(ggplot2)

```

#Load Excel Sheets
```{r echo = FALSE, warning = FALSE, message = FALSE}
#Load in the data from the excel sheet
#KROM Outputs
Model_Sim = read.xlsx(paste(Sys.getenv("KLAMATH_OPS"),"/KROM 2019 PA/Testing/KROM Outputs.xlsx", sep = ""), 
                  sheet=3, colNames=TRUE, cols=2:10, na.strings = "NaN")
Model_Dem = read.xlsx(paste(Sys.getenv("KLAMATH_OPS"),"/KROM 2019 PA/Testing/KROM Outputs.xlsx", sep = ""), 
                  sheet=1, colNames=TRUE, cols=2:9, na.strings = "NaN")
Model_Hyd = read.xlsx(paste(Sys.getenv("KLAMATH_OPS"),"/KROM 2019 PA/Testing/KROM Outputs.xlsx", sep = ""), 
                  sheet=2, colNames=TRUE, cols=2:6, na.strings = "NaN")

#PA Calculator Outputs
PA_Sim = read.xlsx(paste(Sys.getenv("KLAMATH_OPS"),"/KROM 2019 PA/Testing/PA_Calculator_Rev27 Mitch Version.xlsx",
                                sep = ""), sheet=2, colNames=TRUE, cols=2:10)
PA_Dem = read.xlsx(paste(Sys.getenv("KLAMATH_OPS"),"/KROM 2019 PA/Testing/PA_Calculator_Rev27 Mitch Version.xlsx",
                                sep = ""), sheet=3, colNames=TRUE, cols=2:9)
PA_Hyd = read.xlsx(paste(Sys.getenv("KLAMATH_OPS"),"/KROM 2019 PA/Testing/PA_Calculator_Rev27 Mitch Version.xlsx",
                                sep = ""), sheet=4, colNames=TRUE, cols=2:6)
```

#Create Variables for Data Processing and Visualization 
```{r echo = FALSE, warning = FALSE, message = FALSE}
#List general characteristics of the data
NumData = length(Model_Sim[,1])
Dates = seq(as.Date("2019-10-1"), as.Date("2021-02-28"), by="days")
StartDate = as.Date("2020-02-01")

#Vector of plot names
Sim_Names = c("EWA Remain", "EWA Used thru Yesterday", "UKL Outflow", "UKL Release Difference",
                     "UKL Storage", "UKL 5 Day Storage Diff Ratio", "IGD Outflow", "IGD Scheduled Release",
                     "IGD Target Release")
Dem_Names = c("F/FF Pump Offset", "LRDC Offset", "UKL Ag Demand")
Hyd_Names = c("F/FF Pump Accretion", "Keno to IGD Accretion", "Lake Ewuana Accretion", "LRDC Accretion", "UKL Inflow")

#Vector of unit corresponding to the columns
Sim_Units = c("acre-feet", "acre-feet", "cfs", "cfs", "acre-feet", "", "cfs", "cfs", "cfs")
Dem_Units = c("cfs", "cfs", "cfs")
Hyd_Units = c("cfs", "cfs", "cfs", "cfs", "cfs")
```

#Process the Data
```{r echo = FALSE, warning = FALSE, message = FALSE}
#Create a for loop to run through the columns
#This will fill the dataframe with the difference between the two methods
Model_List = list(Model_Sim, Model_Dem, Model_Hyd)
PA_List = list(PA_Sim, PA_Dem, PA_Hyd)
Name_Vctr = c("Sim", "Dem", "Hyd")

for (v in 1:3){
  #Create temporary variables
  Temp_Mod_df = as.data.frame(Model_List[v])
  Temp_PA_df = as.data.frame(PA_List[v])
  No_Col = ncol(Temp_Mod_df)
  mtrx = matrix(0, ncol = No_Col, nrow = NumData)
  diffdf = data.frame(mtrx)
  
  #fill data frame with the differences
  for (i in 1:No_Col){
   for (j in 1:NumData){
      diffdf[j,i] = as.numeric(Temp_Mod_df[j,i]) - Temp_PA_df[j,i]
    }
  }

  #Add a column to the difference dataframe for
  diffdf = add_column(diffdf, Dates, .before = 1) #Dates
  diffdf = add_column(diffdf, 1, .after = (No_Col+1)) #Initial framework for Start Date Identification

  #Set val to 1 or 0 based on if date is after Start Date
  for (i in 1:NumData){
    diffdf[i,(No_Col+2)] = ifelse(diffdf[i,1]<StartDate, 0, 1)
  }

  obsdays = length(which(diffdf[,(No_Col+2)]==0))
  
  #assign temp to the appropiate variable
  assign(paste("diff", Name_Vctr[v], sep=""), diffdf)
}

```

## Simulation Comparison Plots
```{r echo = FALSE}
#Create a for loop to plot the difference between the KROM and PA Calc.
suppressWarnings(
  for (i in 2:10){
    z <- ggplot() + geom_point(data = diffSim[1:obsdays,], aes(x = Dates, y = diffSim[1:obsdays,i], color = "a"), 
                               shape = 18) +
      geom_point(data = diffSim[obsdays:NumData,], aes(x = Dates, y = diffSim[obsdays:NumData,i], color = "b"),
                 shape = 20) +
      scale_color_manual(name = "", values = c("a" = "orangered2", "b" = "royalblue3"),
                         labels = c("Observed", "Projected")) +
      ylab(paste(Sim_Names[(i-1)],"Difference","(", Sim_Units[(i-1)], ")", sep = " ")) +
      ylim((min(diffSim[,i])-0.01), (max(diffSim[,i])+0.01)) +
      xlab("") +
      theme_minimal() +
      theme(legend.position = "none", axis.text = element_text(size = 15), axis.title=element_text(size = 15))
    print(z)
    maxdiff = max(abs(diffSim[,i]), na.rm = TRUE)
    dayofmax = diffSim[which.max(abs(diffSim[,i])),1]
    print(paste("The maximum difference is", maxdiff, "and it occurs on", dayofmax, sep = " "))
})
```

## Demand Comparison Plots
```{r echo = FALSE}
#Create a for loop to plot the difference between the KROM and PA Calc.
suppressWarnings(
  for (i in 2:4){
    z <- ggplot() + geom_point(data = diffDem[1:obsdays,], aes(x = Dates, y = diffDem[1:obsdays,i], color = "a"), 
                               shape = 18) +
      geom_point(data = diffDem[obsdays:NumData,], aes(x = Dates, y = diffDem[obsdays:NumData,i], color = "b"),
                 shape = 20) +
      scale_color_manual(name = "", values = c("a" = "orangered2", "b" = "royalblue3"),
                         labels = c("Observed", "Projected")) +
      ylab(paste(Dem_Names[(i-1)],"Difference","(", Dem_Units[(i-1)], ")", sep = " ")) +
      ylim((min(diffDem[,i])-0.01), (max(diffDem[,i])+0.01)) +
      xlab("") +
      theme_minimal() +
      theme(legend.position = "none", axis.text = element_text(size = 15), axis.title=element_text(size = 15))
    print(z)
    maxdiff = max(abs(diffDem[,i]), na.rm = TRUE)
    dayofmax = diffDem[which.max(abs(diffDem[,i])),1]
    print(paste("The maximum difference is", maxdiff, "and it occurs on", dayofmax, sep = " "))
})
```

## Hydrology Comparison Plots
```{r echo = FALSE}
#Create a for loop to plot the difference between the KROM and PA Calc.
suppressWarnings(
  for (i in 2:6){
    z <- ggplot() + geom_point(data = diffHyd[1:obsdays,], aes(x = Dates, y = diffHyd[1:obsdays,i], color = "a"), 
                               shape = 18) +
      geom_point(data = diffHyd[obsdays:NumData,], aes(x = Dates, y = diffHyd[obsdays:NumData,i], color = "b"),
                 shape = 20) +
      scale_color_manual(name = "", values = c("a" = "orangered2", "b" = "royalblue3"),
                         labels = c("Observed", "Projected")) +
      ylab(paste(Hyd_Names[(i-1)],"Difference","(", Hyd_Units[(i-1)], ")", sep = " ")) +
      ylim((min(diffHyd[,i])-0.01), (max(diffHyd[,i])+0.01)) +
      xlab("") +
      theme_minimal() +
      theme(legend.position = "none", axis.text = element_text(size = 15), axis.title=element_text(size = 15))
    print(z)
    maxdiff = max(abs(diffHyd[,i]), na.rm = TRUE)
    dayofmax = diffHyd[which.max(abs(diffHyd[,i])),1]
    print(paste("The maximum difference is", maxdiff, "and it occurs on", dayofmax, sep = " "))
})
```